%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% LaTeX Template for ECAI Papers 
%%% Prepared by Ulle Endriss (version 1.0 of 2023-12-10)

%%% To be used with the ECAI class file ecai.cls.
%%% You also will need a bibliography file (such as mybibfile.bib).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Start your document with the \documentclass{} command.
%%% Use the first variant for the camera-ready paper.
%%% Use the second variant for submission (for double-blind reviewing).

\documentclass{ecai} 
%\documentclass[doubleblind]{ecai} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Load any packages you require here. 

\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{color}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Define any theorem-like environments you require here.

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{definition}{Definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Define any new commands you require here.

\newcommand{\BibTeX}{B\kern-.05em{\sc i\kern-.025em b}\kern-.08em\TeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frontmatter}

%%% Use this command to specify your submission number.
%%% In doubleblind mode, it will be printed on the first page.

\paperid{123} 

%%% Use this command to specify the title of your paper.

\title{Guidelines for Preparing a Paper for the \\
European Conference on Artificial Intelligence}

%%% Use this combinations of commands to specify all authors of your 
%%% paper. Use \fnms{} and \snm{} to indicate everyone's first names 
%%% and surname. This will help the publisher with indexing the 
%%% proceedings. Please use a reasonable approximation in case your 
%%% name does not neatly split into "first names" and "surname".
%%% Specifying your ORCID digital identifier is optional. 
%%% Use the \thanks{} command to indicate one or more corresponding 
%%% authors and their email address(es). If so desired, you can specify
%%% author contributions using the \footnote{} command.

\author[A]{\fnms{First}~\snm{Author}\orcid{....-....-....-....}\thanks{Corresponding Author. Email: somename@university.edu.}\footnote{Equal contribution.}}
\author[B]{\fnms{Second}~\snm{Author}\orcid{....-....-....-....}\footnotemark}
\author[B,C]{\fnms{Third}~\snm{Author}\orcid{....-....-....-....}} 

\address[A]{Short Affiliation of First Author}
\address[B]{Short Affiliation of Second Author and Third Author}
\address[C]{Short Alternate Affiliation of Third Author}

%%% Use this environment to include an abstract of your paper.

\begin{abstract}

Web page segmentation, the partitioning of a webpage into meaningful blocks, is crucial for various web applications like accessibility evaluation and information extraction. While early methods relied on DOM tree analysis, they often fail to capture the user's visual perception of web content, particularly with modern web technologies. This paper focuses on purely visual web segmentation using the YOLO (You Only Look Once) series. We investigate YOLOv5 and its web segmentation variant, YOLO-WS, previously benchmarked on the visually-labeled Webis-Webseg-20 dataset. We reimplement YOLO-WS, revisit its benchmark performance, and evaluate the latest YOLOv11 architecture against both YOLOv5 and our reimplemented YOLO-WS. Finally, we explore the impact of input resolution on segmentation accuracy for website screenshots.\\

\end{abstract}

\end{frontmatter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
Web segmentation is the task of dividing a web page into meaningful blocks, which is important in applications such as accessibility evaluation, information extraction and web automation. Early web segmentation methods relied heavily on DOM-tree analysis \cite{VIPS, DOM-structure, HEPS}, but faced limitations as DOM structures often fail to represent visual content accurately, especially with modern web development practices using complex CSS and JavaScript transformations.

Recent research increasingly focuses on visual web segmentation, processing the rendered visual representation of web pages directly. While mixed DOM-based models attempt to bridge the gap by combining structural and visual information, the de facto standard dataset for evaluating web segmentation performance is the purely visually labeled dataset Webis-Webseg-20 \cite{kiesel:2020b}. Therefore, this paper focuses on purely visual-based web segmentation methods.

Building upon the promising performance of the YOLO (You Only Look Once) series in visual object detection, this work explores the application of YOLOv5 and its web-segmentation version YOLO-WS proposed by \cite{YOLO-WS} which was benchmarked on Webis-Webseg-20. YOLOv5 is a proprietary model from Ultralytics (unpublished) \cite{yolov5}. However, it is licensed under the AGPL-3.0, making it accessible and modifiable for educational purposes. We seek to reimplement YOLO-WS and revisit benchmarking on Webis-Webseg-20. Additionally, we evaluate the latest YOLOv11 model against YOLOv5 and YOLO-WS, and we hypothesize that increasing input sizes from 512x512 and preserving the images aspect ration could improve performance for website screenshots.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Typeset section headers in sentence case}

You presumably are already familiar with the use of \LaTeX. But let 
us still have a quick look at how to typeset a simple equation: 
%
\begin{eqnarray}\label{eq:vcg}
p_i(\boldsymbol{\hat{v}}) & = &
\sum_{j \neq i} \hat{v}_j(f(\boldsymbol{\hat{v}}_{-i})) - 
\sum_{j \neq i} \hat{v}_j(f(\boldsymbol{\hat{v}})) 
\end{eqnarray}
%
Use the usual combination of \verb|\label{}| and \verb|\ref{}| to 
refer to numbered equations, such as Equation~(\ref{eq:vcg}). 
Next, a theorem: 

\begin{theorem}[Fermat, 1637]\label{thm:fermat}
No triple $(a,b,c)$ of natural numbers satisfies the equation 
$a^n + b^n = c^n$ for any natural number $n > 2$.
\end{theorem}

\begin{proof}
A full proof can be found in the supplementary material.
\end{proof}

Table captions should be centred \emph{above} the table, while figure 
captions should be centred \emph{below} the figure.\footnote{Footnotes
should be placed \emph{after} punctuation marks (such as full stops).}
 
\begin{table}[h]
\caption{Locations of selected conference editions.}
\centering
\begin{tabular}{ll@{\hspace{8mm}}ll} 
\toprule
AISB-1980 & Amsterdam & ECAI-1990 & Stockholm \\
ECAI-2000 & Berlin & ECAI-2010 & Lisbon \\
ECAI-2020 & \multicolumn{3}{l}{Santiago de Compostela (online)} \\
\bottomrule
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Citations and references}

Include full bibliographic information for everything you cite, 
be it a book \citep{pearl2009causality}, a journal article 
\citep{grosz1996collaborative,rumelhart1986learning,turing1950computing}, 
a conference paper \citep{kautz1992planning}, or a preprint 
\citep{perelman2002entropy}. The citations in the previous sentence are 
known as \emph{parenthetical} citations, while this reference to the 
work of \citet{turing1950computing} is an \emph{in-text} citation.
The use of \BibTeX\ is highly recommended. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Use this environment to include acknowledgements (optional).
%%% This will be omitted in doubleblind mode.

\begin{ack}
By using the \texttt{ack} environment to insert your (optional) 
acknowledgements, you can ensure that the text is suppressed whenever 
you use the \texttt{doubleblind} option. In the final version, 
acknowledgements may be included on the extra page intended for references.
\end{ack}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Use this command to include your bibliography file.

\bibliography{mybibfile}

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
